### 2011-02-10 paper/introduction.tex
Added some potentially useful intro text back in
changes
parametrized -> parameterized

\acmFig{robot_close.jpg}{1}{The quadruped robot. The translucent parts were created with 3D-printing technology.}

@@

In this paper we compare the performance of three different methods of designing gaits: manual design, parametrized gaits optimized with seven different learning methods, and gaits generated by evolving neural networks with the HyperNEAT generative encoding~\cite{stanley2009hypercube}. While some of these methods, such as HyperNEAT, have been tested in simulation~\cite{clune2009evolving, clune2011performance}, we investigate how they perform when evolving on a physical robot (\figref{robot_close.jpg}).

@@

>>>>

\acmFig{robot_close.jpg}{1}{The quadruped robot. The translucent parts were created with 3D-printing technology. Videos of the gaits we evolved for this robot can be viewed online~\cite{quadratotWeb}.}

@@

In this paper we compare the performance of three different methods of designing gaits: manual design, parameterized gaits optimized with seven different learning methods, and gaits generated by evolving neural networks with the HyperNEAT generative encoding~\cite{stanley2009hypercube}. While some of these methods, such as HyperNEAT, have been tested in simulation~\cite{clune2009evolving, clune2011performance}, we investigate how they perform when evolving on a physical robot (\figref{robot_close.jpg}).

@@

% Put back in for reference... some good text here I think

% Applications of walking robots often call for the ability to walk as 
% quickly, efficiently, or with as little power as possible.  Often 
% these optimizations are done manually by an expert who designs and 
% tweaks a gait specifically for a given objective.  Other groups have 
% used learning methods to generate gaits optimized for some metric. 
% Approaches differ in their starting assumptions, some essentially 
% tweaking the parameters of a hand-tuned model \cite{chernova}, others 
% exploring a reasonably compact parameter space \cite{kohl}, and still 
% others beginning with few assumptions besides periodicity 
% \cite{zykov}. 
%  
% We aimed to strike a middle ground between these approaches.  Our 
% motion generator did not rely on hand-tweaked gaits, but it did use 
% parameterized gaits which, by their nature, impose some assumptions on 
% the answers produced.  We then used machine learning to design gaits 
% for a quadruped robot with these models.  This paper presents a 
% comparison of the different learning methods implemented.  Most 
% methods created walks that are several times faster than the original 
% hand-tuned gait.  We invite readers with short attention spans to view 
% a video of some of our results online here: 
%  
% 
% %\url{http://www.youtube.com/watch?v=ODoiOj9DdGg} 
% \texttt{http://www.youtube.com/watch?v=ODoiOj9DdGg}
